Carbonate chemistry at Ny-Ålesund

### 2022-01-18 awipev-CO2.Rmd
K1K2 all cleaned up. All good.

  dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite)

@@

                        pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),

@@

-   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
    compared with the uncertainty calculated with seacarb
    (`r round(errors[1, 7], digits = 3)`). In general, pH is
    higher with Sulpis than with Lueker.
-   reasonable for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
    average; always larger with Sulpis than with Lueker) compared with
    the uncertainty calculated with seacarb
    (`r round(errors[1, 8], digits = 1)`)
-   negligible for OmegaAragonite

`r knitr::kable(diff_ls_quant, digits = c(0, 4, 1, 3), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`

>>>>

@@

                        CT = as.numeric(summary(diff_ls2$delta_ct * 1e6)),

@@

-   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
    compared with the uncertainty calculated with seacarb
    (`r round(errors[1, 7], digits = 3)`). In general, pH is
    higher with Sulpis than with Lueker.
-   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
    average; always lower with Sulpis than with Lueker) compared with
    the uncertainty calculated with seacarb
    (`r round(errors[1, 9], digits = 1)`)
-   negligible for OmegaAragonite

`r knitr::kable(diff_ls_quant, digits = c(0, 4, rep(3, 4)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
